\textbf{Autoreduction - an automated data reduction system for beamline instruments at the ISIS Facility}

### 2017-07-12 Documentation/paper/paper.tex
Minor grammar changes and adding ICAT citation

On a successful execuation, the daemon will notify \emph{Reduction Completed} with
the location of the reduced data; otherwise, it will send the reason for
failure to \emph{Reduction Error}, most likely without triggering a
retry. In both cases it will send logs of the process, and clean up
after itself. Some runs associated with the same experiment will write
output to the same directory; to prevent clashes due to this, the node
contains an internal queue holding all jobs associated with a given
experiment for as long as it is actively reducing runs for the
same experiment.

@@

The wholly automated portion of the system revolves around running
scientist-provided scripts to reduce raw instrument data. These scripts
are provided as Python scripts on a per-instrument basis, typically
using the Mantid software package to do the heavy lifting. They're
stored on a shared file store in a known location, where they can be
modified at will by instrument scientists and the script used in
reduction is stored in the system database.

Aside from overall logic, these scripts typically require parameters
such as calibration files, information about how the instrument was run,
output settings, and so on. A mechanism for providing such parameters 
separate from the script itself is provided. A list of parameters and
default values is provided in a Python file similar to the reduction
script, and the autoreduction system keeps track of the parameter
configurations provided to it, and applies them to the relevant jobs.

The scripts need to integrate with the automation system, and
as such must conform to a certain specification: a reduction script must have a
\emph{main()} method, taking an input data file and an output directory as
arguments. If the script uses system-supplied parameters, it must have a
certain \emph{import} directive, which serves as a point of injection
for the variables when the reduction script is executed.

A reduction script is a Python script and it can call any software 
callable from Python installed on the reduction worker compute nodes,
including Mantid data reduction algorithms.

Each experiment at ISIS has a unique so-called RB-number
and for almost all experiments at ISIS multiple separate runs are collected.
A reduction script has access to all reduced data for an experiments, which 
may be used in a script to automatically combine information from multiple 
data reductions.

at ISIS has access to previously reduced data can be a stupid and clever as an instrument
scientists wants it to be. For example

@@

The web app provides the user-facing interface for managing reduction.
It was developed in Python, using the Django web framework, and is
integrated (SHOULD WE BE MORE SPECIFIC ABOUT WHAT INTEGRATION
MEANS HERE - THE READER MAY BE CONFUSED ABOUT THIS) with the state database.

Users log in via the ISIS User Office system -- using credentials 
granted for facility-wide use -- and their level of access is then 
governed by ICAT's information on the experiments and instruments they 
should be able to see. A searchable index of the runs is displayed on the front page, sorted
by instrument, experiment (RB-number) and/or run number, showing their reduction
status.

Each run has its own summary page with detailed information; a user can
see the status of the reduction, where the reduced data is, and the
script and variables that were used to reduce it. From here the run can
be re-run, with or without modifying the variables used. Any
experimenter can access this page for their runs, and it is intended that
external scientists running experiments be able to control their data
reduction directly in this way.

Experiments also have summary pages, showing all the runs that are
associated with a given experiment along with their status and data
locations. Metadata about the experiment is retrieved from ICAT and
displayed here.

Instrument scientists can access a summary page for their instruments,
showing the current status of runs on an instrument, as well as current
and upcoming run variables. From here instrument scientists can assign
sets of variables by experiment and run number, which will then be used
for new runs. Batch re-running of past jobs
is also possible here. This option allows instrument scientists
the convenience of re-running multiple failed jobs should this be required.

Administrators can access everything above, and additionally have access
to pages displaying all queued and failed jobs. These pages provide an
overview of the status of the system at a glance, and have controls for
batch operations on failed jobs such as to re-run them.

>>>>

On a successful execution, the daemon will notify \emph{Reduction Completed} with
the location of the reduced data; otherwise, it will send the reason for
failure to \emph{Reduction Error}, most likely without triggering a
retry. In both cases, it will create logs of the process and also clean up
after itself. Some runs associated with the same experiment will write
output to the same directory; to prevent clashes due to this, the node
contains an internal queue holding all jobs associated with a given
experiment for as long as it is actively reducing runs for the
same experiment.

@@

The wholly automated portion of the system revolves around running
scientist-provided scripts to reduce raw instrument data. These scripts
are provided as Python scripts on a per-instrument basis, typically
using the Mantid software package to do the heavy lifting. They're
stored on a shared file store in a known location where they can be
modified at will by instrument scientists. The script used in
reduction is also stored in the system database.

Aside from overall logic, these scripts typically require parameters
such as calibration files, information about how the instrument was run,
output settings, and so on. A mechanism for providing such parameters 
separate from the script itself is provided. A list of parameters and
default values is provided in a Python file similar to the reduction
script. The autoreduction system keeps track of the parameter
configurations provided to it and applies them to the relevant jobs.

The scripts need to integrate with the automation system, and
as such must conform to a certain specification: a reduction script must have a
\emph{main()} method, taking an input data file and an output directory as
arguments. If the script uses system-supplied parameters, it must have a
certain \emph{import} directive which serves as a point of injection
for the variables when the reduction script is executed.

A reduction script is a Python script and it can call any software 
callable from Python installed on the reduction worker compute nodes which
includes Mantid data reduction algorithms.

Each experiment at ISIS has a unique so-called RB-number
and for almost all experiments at ISIS multiple separate runs are collected.
A reduction script has access to all reduced data for an experiment, which 
may be used in a script to automatically combine information from multiple 
data reductions.

@@

The web app provides the user-facing interface for managing reduction.
It was developed in Python, using the Django web framework, and is
integrated with the state database. Django provides an intuitive way to
interact with databases through its use of models and Object Relational Mapping (ORM).
Therefore, getting information from the database to show on the front end is 
quick and intuitive.

Users log in via the ISIS User Office system -- using credentials 
granted for facility-wide use -- and their level of access is then 
governed by ICAT's \cite{icat} information on the experiments and instruments they 
should be able to see. A searchable index of the runs is displayed on the front page, sorted
by instrument, experiment (RB-number) and/or run number, showing their reduction
status.

Each run has its own summary page with detailed information; a user can
see the status of the reduction, where the reduced data is, and the
script and variables that were used to reduce it. From here the run can
be re-run, with or without modifying the variables used and with the choice
of whether or not to overwrite the previous run's data. Any
experimenter can access this page for their runs, and it is intended that
external scientists running experiments would be able to control their data
reduction directly in this way.

Experiments also have summary pages, showing all of the runs that are
associated with a given experiment along with their status and data
locations. Metadata about the experiment is retrieved from ICAT and
displayed here.

Instrument scientists can access a summary page for their instruments,
showing the current status of runs on an instrument, as well as current
and upcoming run variables. From here, instrument scientists can assign
sets of variables by experiment and run number which will then be used
for new runs. Batch re-running of past jobs is also possible here. 
This option allows instrument scientists the convenience of re-running multiple 
failed jobs should this be required.

Administrators can access everything above and additionally have access
to pages displaying all queued and failed jobs. These pages provide an
overview of the status of the system at a glance and have controls for
batch operations on failed jobs such as to re-run them.
